### 2016-07-08 overlay_fs.tex
Structural changes: Moving HTTP to the Appendix and some editing

Again, if for some reason, the \texttt{-P} option is not available for
\texttt{losetup}, we provide an alternative command line in
Section~\ref{sec:alternative_losetup}. Finally, if the previous filesystem
formatting was successful, the filesystem is now available for use. Thus,
we need to inform the Raspbian root filesystem to mount the home partition
that we have just created. We will notify to the Raspbian \ac{OS} during
the startup of the \ac{Raspi}s. This can be done by adding an entry in
\texttt{fstab} as follows:

@@

That is it. unmount partitions and detach loop device:
\begin{lstlisting}[]
# umount --recursive ${ROOTDIR}
# losetup -d ${DEV}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

\subsection{Write image to memory card}

EMPHASIZE THAT THIS SETUP IS ONLY FOR THE SETUP WHERE THE ROOT IMAGE ARE
WRITTEN TO THE MEMORY CARDS

The final step is to write the image to all the memory cards before they can
be used in the \ac{Raspi}s.

%This is done by first leaving the \texttt{chrooted}
%filesystem and unmounting all the directories we mounted:

% Exit chroot, umount, and write to memory card
%\begin{lstlisting}[]
%# exit
%# cd ..
%# umount --recursive ${ROOTDIR}
%# losetup -d ${DEV}.img
%\end{lstlisting}
%\FloatBarrier
%\vspace{-5mm}

%If successfully unmounted, you can
Insert a memory card in your machine. It will be available as
\texttt{/dev/mmcblkX} or \texttt{/dev/sdX}

>>>>

Again, if for some reason, the \texttt{-P} option is not available for
\texttt{losetup}, we provide an alternative command line in
Section~\ref{sec:alternative_losetup}. Finally, if the previous filesystem
formatting was successful, the filesystem is now available for use. Thus,
we need to inform the Raspbian \ac{OS} to mount the home partition
that we have just created. We will notify the \ac{OS} while
booting during the startup of the \ac{Raspi}s. This can be done by adding
an entry in \texttt{fstab} as follows:

@@

Now, unmount again all the partitions and detach the loop devices as follows:
\begin{lstlisting}[]
# umount --recursive ${ROOTDIR}
# losetup -d ${DEV}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

If the steps have been properly made up to this point, the customized image
is ready to be deployed into the \ac{Raspi}s. In the following section, we
indicate how to proceed with the writing of the image into various memory
cards, although a more complex setup with a \ac{HTTP} server is also presented
in Section~\ref{sec:http} of the Appendix.

\subsection{Customized Image Writing to Memory Cards}
For a basic system setup, the final step is to write the customized image
to all the memory cards before they can be used in the \ac{Raspi}s. For
our current considered system, we do this manually for each card. Insert
a memory card in your machine. It will be available as \texttt{/dev/mmcblkX}
or \texttt{/dev/sdX}.
